\documentclass[11pt]{article}
\title{Cover Letter}
\author{Harry Han}
\date{\today}

\begin{document}
\maketitle

I am a mathematician by training. Currently in the third year of my undergraduate degree, I have acquired rigorous knowledge, in addition to various topics in pure mathematics, in statistics, probability, and numerical methods, all of which are foundation of modern industrial research.

In addition to mathematics, chemistry is also of my passion.
In the first two years of the university, I have taken the full course load of the pre-honours curriculum of Chemistry and obtained good grades, in additional to complete the regular course work of mathematics. 
In high school, I have conducted research on photochemistry under the guidance of Dr Frank Gasparro, then my chemistry teacher. We have obtained promising results, on which a provisional patent was filed to USTPO. 

I am also a self-taught computer scientist. I am comfortable writing large-scale programming projects using various programming languages and technologies including C and C++. I have contributed to various open source project, including linux, i3, and vim. Currently, I am part of Dr Antonio Barbalace's research group investigating on linux operation system and computer architecture.
Although I have limited experience in robotics, I am confident that I can quickly pick up the necessary skills to contribute to the project.

In conclusion, I believe my expertise in mathematics, knowledge in chemistry, and practical skills in programming, coupled with my inquisitive and self-driven character, will make me suitable for this internship.
\end{document}

