\documentclass[10pt, a4paper]{article}

\usepackage{xcolor, hyperref}
\hypersetup{colorlinks,linkcolor={red!40!black},citecolor={blue!50!black},urlcolor={blue!80!black}}
% \usepackage[
%     ignoreheadfoot, % set margins without considering header and footer
% 	top=5 cm,
%     left=2.5 cm, % separation between body and page edge from the left
%     right=2.5 cm, % separation between body and page edge from the right
%     footskip=1.0 cm, % separation between body and footer
%     % showframe % for debugging 
% ]{geometry} % for adjusting page geometry


% FONT
\usepackage{charter}
\setlength{\columnsep}{0.15cm} % set column separation
\renewcommand{\baselinestretch}{1.1}

\pagenumbering{gobble}

\begin{document}

Yuhao Han (Harry)
\vspace{0.5cm}

+44 7769466855

s2162783@ed.ac.uk
\vspace{0.5cm}

30 Oct, 2024

\vspace{0.5cm}
Dear Sir or Madam,

I am excited to know that Revolut will offer Python software engineer internship opportunities within Rev-celerator Internship Programme. 
I believe I can be a good fit for this role.

Although I am an undergraduate student studying mathematics in the University of Edinburgh, I have self-studied extensively in computer science. 
I am familiar Python and API development. 
Previously, I have built a Python API backend via FastAPI and Django for \href{https://joblist.org.uk}{joblist.org.uk}, my yet to be successful start up attempt.

My other coding experience includes several side projects: 
\href{https://github.com/harryhanYuhao/lox-rust}{lox}, an interpreter from scratch in Rust,
\href{https://github.com/harryhanYuhao/aformatter}{aformatter}, a x86-64 assembly formatter in C,
and \href{https://github.com/harryhanYuhao/KitchenChaos}{Kitchen Chaos}, a 3D game made with Unity.
I am also an active open-source contributor.
I have reviewed and edited documentations for Rust, created two rust packages on crate.io, filed issues and bug reports for mdbook, vim, and Nextjs, and contributed to the Linux kernel.

You may wonder why I chose to study mathematics in the university but spent so much efforts in computer science.
The reason is that mathematics is my primary interest,
and, while enjoying the abstract side of mathematics, I am shocked to find how closely these abstract theories, regardless of how surreal or theoretical, upon slight modifications, can be used to solve real world problems otherwise unsolvable. 
Two of the prime examples are Fourier transformation in electric engineering and quaternions in 3D graphics.
The sad reality, however, is that much of the rich mathematics have been inaccessible to non-mathematicians, and much of the potentials have not been discovered. 
By studying computer science, I hope I may close some of the gaps.

As to my eligibility, I am currently in year four of the five year MMath (Hons) program in the University of Edinburgh, 
I am fluent in English with TOEFL score of 115/120,
and I will be able to work full time in-person or hybrid in the London over the summer of 2025.

Thank you for your time and I will look forward to your response.

\vspace{0.5cm}
Yours sincerely
\vspace{0.5cm}

Yuhao Han

\end{document}

